Inference methods comparison for the simplified Naomi model using the Kolmogorov-Smirnov test statistic

### 2023-07-21 src/naomi-simple_ks/ks.Rmd
Better KS summary plot (still some workshopping to go), worst parameters automatically plotted #55

dict <- data.frame(
  parname = c(unique(x_names), unique(theta_names)),
  type = c(rep("Latent field", length(unique(x_names))), rep("Hyper", length(unique(theta_names))))
)

@@

ks_summary <- ks_df %>%
  group_by(method, parname, type) %>%
  summarise(ks = signif(mean(ks), 4)) %>%
  pivot_wider(names_from = "method", values_from = "ks") %>%
  rename(
    "Parameter" = "parname",
    "KS(aghq, tmbstan)" = "aghq",
    "KS(TMB, tmbstan)" = "TMB",
  )

@@

ks_summary %>%
  filter(type != "Hyper") %>%
  ks_plot_many("TMB", "aghq")
```

```{r}
ks_summary %>%
  group_by(type) %>%
  summarise(
    TMB = mean(`KS(TMB, tmbstan)`),
    aghq = mean(`KS(aghq, tmbstan)`)
  ) %>%
  gt::gt()
```

@@

```{r}
ks_summary %>%
  filter(type == "Latent field") %>%
  mutate(diff = signif(`KS(TMB, tmbstan)` - `KS(aghq, tmbstan)`, 3)) %>%
  DT::datatable()
```

@@

```{r}
ks_df_wide %>%
  arrange(desc(diff)) %>%
  head(n = 10)

histogram_and_ecdf(par = "us_alpha_xs", i = 18)
histogram_and_ecdf(par = "us_alpha_xs", i = 16)
histogram_and_ecdf(par = "u_alpha_xs", i = 13)
```

@@

```{r}
ks_df_wide %>%
  arrange(diff) %>%
  head(n = 10)

histogram_and_ecdf(par = "ui_anc_rho_x", i = 27)
histogram_and_ecdf(par = "ui_anc_alpha_x", i = 19)
histogram_and_ecdf(par = "u_alpha_x", i = 18)
```

>>>>

dict <- data.frame(
  parname = c(unique(x_names), unique(theta_names)),
  type = c(rep("Latent", length(unique(x_names))), rep("Hyper", length(unique(theta_names))))
)

@@

ks_summary <- ks_df %>%
  group_by(method, parname, type) %>%
  summarise(
    ks = mean(ks),
    size = n()
  ) %>%
  pivot_wider(names_from = "method", values_from = "ks")

@@

extended_cbpalette <- colorRampPalette(multi.utils::cbpalette())

ks_summary_latent <- filter(ks_summary, type == "Latent field")

xy_length <- min(1, max(ks_summary_latent$aghq, ks_summary_latent$TMB) + 0.03)

ks_summary_latent %>%
  ggplot(aes(x = TMB, y = aghq, col = parname, size = size)) +
  geom_point(alpha = 0.4) +
  xlim(0, xy_length) +
  ylim(0, xy_length) +
  scale_color_manual(values = extended_cbpalette(n = 20)) +
  scale_size_continuous(breaks = c(2, 10, 32), labels = c(2, 10, 32)) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  labs(x = "KS(TMB, NUTS)", y = "KS(PCA-AGHQ, NUTS)", col = "Parameter", size = "Length", subtitle = "Smaller KS values indicate higher accuracy") +
  theme_minimal() +
  guides(size = guide_legend(title.position = "top", direction = "vertical"), col = guide_legend(title.position = "top")) +
  theme(legend.position = "bottom", legend.title = element_text(size = rel(0.9)), legend.text = element_text(size = rel(0.7)))

ggsave("ks-summary.png", h = 5, w = 6.25, bg = "white")
```

```{r}
ks_summary %>%
  group_by(type) %>%
  summarise(
    TMB = mean(TMB),
    aghq = mean(aghq)
  ) %>%
  gt::gt()
```

@@

```{r}
ks_summary %>%
  filter(type == "Latent") %>%
  mutate(diff = signif(TMB - aghq, 3)) %>%
  DT::datatable()
```

@@

```{r}
(tmb_beats_aghq <- ks_df_wide %>%
  filter(!is.na(type)) %>%
  arrange(diff) %>%
  head(n = 10))

histogram_and_ecdf(par = tmb_beats_aghq$parname[1], i = tmb_beats_aghq$index[1])
histogram_and_ecdf(par = tmb_beats_aghq$parname[2], i = tmb_beats_aghq$index[2])
histogram_and_ecdf(par = tmb_beats_aghq$parname[3], i = tmb_beats_aghq$index[3])
```

@@

```{r}
(aghq_beats_tmb <- ks_df_wide %>%
  filter(!is.na(type)) %>%
  arrange(desc(diff)) %>%
  head(n = 10))

histogram_and_ecdf(par = aghq_beats_tmb$parname[1], i = aghq_beats_tmb$index[1])
histogram_and_ecdf(par = aghq_beats_tmb$parname[2], i = aghq_beats_tmb$index[2])
histogram_and_ecdf(par = aghq_beats_tmb$parname[3], i = aghq_beats_tmb$index[3])
```
